Language Use in a Multilingual Tweet Corpus

### 2018-07-18 paper.tex
Final changes

However, the question of whether the collection is any good remains open. It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data. But does not reveal its intrinsic properties. Nevertheless, we believe the presented dataset is useful across different studies.

>>>>

%However, the question of whether the collection is any good remains open. It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data. But does not reveal its intrinsic properties. Nevertheless, we believe the presented dataset is useful across different studies.
